The regularity of ODEs and thimble integrals \\ with respect to Borel summation

### 2024-04-16 exp-resurgence.tex
Finish revising "Thimble integrals in geometry"

% \subsubsection{\textcolor{orange}{[M.A.E.T. section]}}
% Although it is not contructive, the Main Asymptotic Existence Theorem (M.A.E.T.) guarantees the existence of a frame of analytic solutions asymptotic to Poincar\'{e}'s formal ones~\cite[Chapter~14]{balser}. The Ramis Index Theorem shows that the formal solutions are 1-Gevrey series---the first step in proving Borel~summability~\cite{ramis_index}. \textcolor{orange}{[Revise\ldots]} \textcolor{RoyalBlue}{Furthermore, after checking the solution $\series{\Phi}$ is Borel summable, another argument is needed to show that the Borel sum solve the original equation---a priori, the Borel sum is only Gevrey asymptotic to the solution $\series{\Phi}$.}
\subsubsection{\'{E}calle's theory of resurgence}
\color{DarkBlue}
\'{E}calle's theory of resurgence introduced a new perspective on formal solutions, mostly focused on the analysis of the position domain~\cite{EcalleIII,loday-Remy2011}. In a nutshell, resurgence provides information about the analytic continuation of the Borel transform of a divergent series. In particular, it reveals the locations of singularities in the position domain, and it quantifies the Stokes phenomenon in terms of ``Stokes constants'' describing analytic continuation around the singularities.

@@

\textcolor{orange}{[Kontsevich and Soibelman: Riemann-Hilbert problem in analytic frequency domain from Stokes constants in the formal position domain. New section?]}
\color{RoyalBlue}\par
The developement of \'Ecalle's theory of resurgence introduced a new approach to the study of formal solutions, mostly focused on the analysis of the position domain~\cite{EcalleIII,loday-Remy2011}.

In a nutshell, the aim of resurgence is to study the analytic continuation of the Borel transform of a divergent series, in particular the location of sngularities in the position domain and Stokes constants computed after analytic continuation across the singularities.

Recall, that resurgent $1$-Gevrey series have an endlessly analytically continuable Borel transform. Thus resurgence makes naturally a bridge between formal and analytic solutions in the position domain. Indeed, differential equations in the frequency domain can be turned into integral equations in the position domain, using the Borel transform. In particular the Borel transform of the formal solution $\series{\Phi}_\alpha$ is a convergent power series, and its sum can be studied by in terms of the equation it satisfies. For instance, in~\cite{loday-Remy2011}, Loday-Richaud and Remy solve perturbed integral equations formally in the position domain (following the approach of \'Ecalle~\cite{EcalleIII}). Yet working in the position domain, one can turn the integral equation into a differential equation and trying to solve it analytically in the position domain, see~\cite{malgrange--fourier}. Then, going back to the frequency plane can be done with the Laplace transform, but it is usually a technincal analytic step.

However, more absractly, taking as input the set of Stokes data (namely the Stokes ray emanating from the singulairties and the associated Stokes constants) one can set-up a Riemann--Hilbert problem, whose solution would give a frame of analytic solutions of the ODEs~\cite{kontsevich2022analyticity}. This is an advantage of resurgence techniques compared to the usual Borel summation method. 
\color{black}
% Then, the Stokes phenomenon is another distiguishd feature of irregular singular ODEs, an it is closely related to the fact that formal solutions are divergent. 
% Indeed, the so called Stokes constants encode the ``jumps" of the underlying analytic solution which are charcateriz to have different asymptotics in different sectors saparated by Stokes lines. and when extended by continuation on larger sectors it jumps by an exponentially small correction. As an example, the first order equation \[\Phi'=\Phi+\frac{1}{z}\] has formal solution $\series{\Phi}=\sum_{n=0}^\infty n!z^{-n-1}$. Then, its Borel transform has a simple pole at $\zeta=1$. Consequently, the ``jump'' of its Borel sum occurs across the positive real axis $\Re(z)>0$ and it is given by $2\pi ie^{-z}$.

% Still based on Borel summation, the approach of resurgence introduced by \'Ecalle in the '80 emphasizes the role of the position domain. Indeed, differential equation in the frequency domain can be turned into integral equation in the position domain, using the Borel transform. In particular the Borel transform of the formal solution $\series{\Phi}$ is a germ of analytic functions, and its analytic properties can be studied in terms of the equation they satisfy. For instance, in~\cite{loday-Remy2011}, Loday-Richaud and Remy solve perturbed integral equations formally in the position domain (following the approach of \'Ecalle~\cite{EcalleIII}). Yet working in the position domain, one can turn the integral equation into a differential equation and trying to solve it analytically in the position domain, see~\cite{malgrange--fourier}. Then, going back to the frequency plane can be done with the Laplace transform, but it is usually a technincal analytic step.

\subsubsection{Laplace transform methods and fixed point iteration}
All of the historical approaches we have discussed so far start by looking for formal solutions. In this paper, we will focus on a different kind of approach, where we start by looking for analytic solutions expressed as Laplace transforms. By carefully choosing the starting point of the Laplace transform, we get analytic solutions which are asymptotic to Poincar\'{e}'s formal ones. These solutions will turn out to be Borel regular.
% \par \textcolor{RoyalBlue}{So far we have been discussing the classical approaches to summability and reusrgence of formal divergent solutions of irregular singular ODEs, but a different approach would be to look for analytic solutions of $\mathcal{P}\Phi=0$. In other words, we can solve irregular singular ODEs in the frequency domain starting with an analytic \emph{ansatz}. Here the standard approach is the so called Laplace method, which takes as \emph{ansatz} a Laplace transform integral. This is the approach we adopt in this paper, but our choice of Laplace transform integral is very special, i.e. it is a Borel regular solution.} 
We use the Laplace transform to turn differential equations on the frequency domain into integral equations on the position domain. This runs parallel to \'{E}calle's use of the Borel transform. Building on the existence and uniqueness results we proved in~\cite{reg-sing-volterra}, we use Picard iteration to solve the integral equation in the position domain, and to show that the corresponding solution in the frequency domain is Borel regularizable.%\textcolor{RoyalBlue}{Like in \'Ecalle's method, the Laplace transform method turns differential equations in the frequency domain into integral equations in the position domain. Then, building on our existence and uniqueness results of~\cite{reg-sing-volterra}, we show that analytic solutions of the Laplace transformed ODE can be computed with Picard iteration.} %In addition, as we will show in Section~\ref{sec:new-summability-proof}.

@@

% In Section~\ref{borel_reg-ODE}, we show that we are all finding the same frame. The uniqueness part of \cite[Theorem~4]{reg-sing-volterra} shows that \'{E}calle's formal solutions sum to our analytic ones, and Theorem~\ref{thm:exist_uniq_ODE} guarantees that our solutions are asymptotic to Poincar\'{e}'s ones.
% \end{remark} 
%
%
%
\subsection{Borel regularity for thimble integrals}
%
Thimble integrals have been studied from different perspectives: in physics, they play an important technical role in quantum mechanics, where infinite-dimensional exponential integrals are supposed to give the expectation values of observable quantities \cite{dunne-unsal2,dunne-unsal,Fauvet_Menous_Queva,Tanizaki:2014tua}. In the algebraic geometric set-up, namely when, following the notation introduced in Section~\ref{borel-reg:explanatory-power}, $X$ is an $N$-dimensional alegbraic variety over $\C$ and $f$ is a proper map $f\colon X\to\C$, thimble integrals are known as period integrals \cite{deligne2007singularites,Maxim_lectures,pham}.\footnote{In particular, they find application in mirror symmetry for Fano varieties as they encode the Gromov--Witten invariants.\textcolor{orange}{add references---Maxim's mirror symmetry talk, Varchenko}.}
\subsubsection{Thimble integral in physics}

\subsubsection{Thimble integral in geometry}
\color{DarkBlue}
Thimble integrals can be used to explore the geometry of complex manifolds, and even to define a homology theory. To see how this works, we first recall how the one-dimensional definition of a Lefschetz thimble arises from the general definition. Suppose that $f \maps X \to B$ is a holomorphic map from an $N$-dimensional complex manifold $X$ to a translation surface $B$. Consider a translation chart $\zeta$ on $B$ and a non-degenerate critical point $a \in X$ that $f$ sends to $\zeta = \alpha$. Near $a$, we can always find coordinates $t_1, \ldots, t_N$ on $X$ with
\[ f^*\zeta = \alpha + e^{i \theta} (t_1^2 + \ldots + t_N^2). \]
Each such coordinate system defines a Lefschetz thimble: the oriented real-analytic submanifold where $t_1, \ldots, t_N$ are real. There are many such coordinate systems, but they are all related by local holomorphic maps from $X$ to the complex orthogonal group $O_N(\C)$. Since $O_N(\C)$ has only two connected components, distinguished by the sign of the determinant, a Lefschetz thimble is determined up to homotopy and orientation by the critical point $a$ and the direction $\theta$. When $N = 1$, the homotopy freedom disappears, because $O_1(\C)$ is the discrete group $\{\pm 1\}$.

\color{BlueViolet}
\begin{itemize}
\item Explain how can be seen in terms of homology (cite Pham).
\end{itemize}
\color{black}
%
\subsubsection{Asymptotics of thimble integrals}
%
\textcolor{orange}{[Revise\ldots]}
\color{DarkTurquoise}\par
Classical examples of $1$-dimensional thimble integrals (with polynomial $f$) are special functions, thus the Borel summability properties of their asymptotics can be studied either analytically (through the \textit{thimble projection reasoning} see the discussion in Section~\ref{sec:examples}) or geometrically (in terms of a certain Riemann--Hilbert problem \cite{Maxim_slide_ERC}\cite[Section 6.2]{kontsevich2022analyticity}).

@@

\color{RoyalBlue}
Thimble integrals have been studied from different perspectives: in physics, they play an important technical role in quantum mechanics, where infinite-dimensional exponential integrals are supposed to give the expectation values of observable quantities \cite{dunne-unsal2,dunne-unsal,Fauvet_Menous_Queva,Tanizaki:2014tua}. In this context, physicists often use Borel summation, resurgence and related techniques to assign values to these integrals going beyond their pertubative expansion (see also \cite{Berry_Howls,Berry1991,costin_kruskal,Howls97,Howls,pham1988resurgence}). For instance, in complex Chern--Simons theory, one could decompose the path integral in thimble integrals and arguing as in the finite dimesional set-up to study the Witten--Reshetikhin--Turaev invariants of $3$ manifolds \cite{gukov-marino-purtrov-resurgence,Witten}. \textcolor{orange}{Take a look at Witten's paper on knots} More generally, we could think of a problem that is known to admit a thimble integral solution but that's hard to be defined explicitly. However, we know the perturbative expansion of the expected solution; then Borel regularity tells us that the Borel sum of the pertubative series is the solution we are looking for. In fact, the Laplace transform ray (namely the ray along which the Laplace trasnform is defined) is often a ``collapsed'' thimble.\textcolor{Maroon}{This is the bit about turning a perturbative series back into a thimble integral, taking advantage of the fact that the Laplace transform ray is often a ``collapsed'' thimble.}

@@

The Laplace transform $\laplace^\theta_{\zeta,\alpha}$ is a homomorphim from the algebra of locally integrable, exponentially bounded holomorphic functions, equipped with the convolution product, to the algebra of analytic functions on the half-plane $\Re(e^{i\theta} z) > 0$, equipped with the usual product.

@@

For $\alpha=0$, the Definition~\label{def:convolution} agrees with the standard deifinition of convolution \cite[Definition~5.12]{diverg-resurg-i}.
In addition, we will denote $\ast_{\zeta,0}$ simply by \textcolor{magenta}{$\ast$ [coordinate is necessary]}, following the standard convention.   
Notice that, assuming the Taylor expansion of $\phi$ and $\psi$ at $\zeta=\alpha$ are convergent in a disk of radius $R$, then the convolution $\phi\ast_{\zeta,\alpha}\psi$ has a convergent Taylor expansion at $\zeta=\alpha$ in the disk of radius $R$ (when $\alpha=0$, see \cite[Lemma 5.14]{diverg-resurg-i} for a proof).

>>>>

% \subsubsection{\textcolor{orange}{[M.A.E.T. section]}}
% Although it is not contructive, the Main Asymptotic Existence Theorem (M.A.E.T.) guarantees the existence of a frame of analytic solutions asymptotic to Poincar\'{e}'s formal ones~\cite[Chapter~14]{balser}. The Ramis Index Theorem shows that the formal solutions are 1-Gevrey series---the first step in proving Borel~summability~\cite{ramis_index}. \textcolor{orange}{[Revise\ldots]} \textcolor{RoyalBlue}{Furthermore, after checking the solution $\series{\Phi}$ is Borel summable, another argument is needed to show that the Borel sum solve the original equation---a priori, the Borel sum is only Gevrey asymptotic to the solution $\series{\Phi}$.}
\subsubsection{\'{E}calle's theory of resurgence}
\'{E}calle's theory of resurgence introduced a new perspective on formal solutions, mostly focused on the analysis of the position domain~\cite{EcalleIII,loday-Remy2011}. In a nutshell, resurgence provides information about the analytic continuation of the Borel transform of a divergent series. In particular, it reveals the locations of singularities in the position domain, and it quantifies the Stokes phenomenon in terms of ``Stokes constants'' describing analytic continuation around the singularities.

@@

\textcolor{orange}{[Kontsevich and Soibelman: Riemann-Hilbert problem in analytic frequency domain from Stokes constants in the formal position domain. New section?]}
\color{RoyalBlue}\par
However, more absractly, taking as input the set of Stokes data (namely the Stokes ray emanating from the singulairties and the associated Stokes constants) one can set-up a Riemann--Hilbert problem, whose solution would give a frame of analytic solutions of the ODEs~\cite{kontsevich2022analyticity}. This is an advantage of resurgence techniques compared to the usual Borel summation method. 
\color{black}
%
\subsubsection{Laplace transform methods and fixed point iteration}
%
All of the historical approaches we have discussed so far start by looking for formal solutions. In this paper, we will focus on a different kind of approach, where we start by looking for analytic solutions expressed as Laplace transforms. By carefully choosing the starting point of the Laplace transform, we get analytic solutions which are asymptotic to Poincar\'{e}'s formal ones. These solutions will turn out to be Borel regular.
% \par \textcolor{RoyalBlue}{So far we have been discussing the classical approaches to summability and reusrgence of formal divergent solutions of irregular singular ODEs, but a different approach would be to look for analytic solutions of $\mathcal{P}\Phi=0$. In other words, we can solve irregular singular ODEs in the frequency domain starting with an analytic \emph{ansatz}. Here the standard approach is the so called Laplace method, which takes as \emph{ansatz} a Laplace transform integral. This is the approach we adopt in this paper, but our choice of Laplace transform integral is very special, i.e. it is a Borel regular solution.} 
We use the Laplace transform to turn differential equations on the frequency domain into integral equations on the position domain. This runs parallel to \'{E}calle's use of the Borel transform. Building on the existence and uniqueness results we proved in~\cite{reg-sing-volterra}, we use Picard iteration to solve the integral equation in the position domain, and to show that the corresponding solution in the frequency domain is Borel regularizable.%\textcolor{RoyalBlue}{Like in \'Ecalle's method, the Laplace transform method turns differential equations in the frequency domain into integral equations in the position domain. Then, building on our existence and uniqueness results of~\cite{reg-sing-volterra}, we show that analytic solutions of the Laplace transformed ODE can be computed with Picard iteration.} %In addition, as we will show in Section~\ref{sec:new-summability-proof}.

@@

% In Section~\ref{borel_reg-ODE}, we show that we are all finding the same frame. The uniqueness part of \cite[Theorem~4]{reg-sing-volterra} shows that \'{E}calle's formal solutions sum to our analytic ones, and Theorem~\ref{thm:exist_uniq_ODE} guarantees that our solutions are asymptotic to Poincar\'{e}'s ones.
% \end{remark} 
%
%
%
\subsection{Borel regularity for thimble integrals}
%
Thimble integrals have been studied from different perspectives: in physics, they play an important technical role in quantum mechanics, where infinite-dimensional exponential integrals are supposed to give the expectation values of observable quantities \cite{dunne-unsal2,dunne-unsal,Fauvet_Menous_Queva,Tanizaki:2014tua}. In the algebraic geometric set-up, namely when, following the notation introduced in Section~\ref{borel-reg:explanatory-power}, $X$ is an $N$-dimensional alegbraic variety over $\C$ and $f$ is a proper map $f\colon X\to\C$, thimble integrals are known as period integrals \cite{deligne2007singularites,Maxim_lectures,pham}.\footnote{In particular, they find application in mirror symmetry for Fano varieties as they encode the Gromov--Witten invariants.\textcolor{orange}{add references---Maxim's mirror symmetry talk, Varchenko}.}
\subsubsection{Thimble integrals in physics}

\subsubsection{Thimble integrals in geometry}
Thimble integrals can be used to explore the geometry of complex manifolds, and even to represent elements of a homology group. To see how this works, we first recall how the one-dimensional definition of a Lefschetz thimble arises from the general definition. Suppose that $f \maps X \to B$ is a holomorphic map from an $N$-dimensional complex manifold $X$ to a translation surface $B$. Consider a translation chart $\zeta$ on $B$ and a non-degenerate critical point $a \in X$ that $f$ sends to $\zeta = \alpha$. Near $a$, we can always find coordinates $t_1, \ldots, t_N$ on $X$ with
\[ f^*\zeta = \alpha + e^{i \theta} (t_1^2 + \ldots + t_N^2). \]
When the ray $\mathcal{J}_{\zeta, \alpha}^\theta$ avoids the other critical values of $f$, each such coordinate system defines a Lefschetz thimble: the oriented real-analytic submanifold where $t_1, \ldots, t_N$ are real. There are many such coordinate systems, but they are all related by local holomorphic maps from $X$ to the complex orthogonal group $O_N(\C)$. Since $O_N(\C)$ has only two connected components, distinguished by the sign of the determinant, a Lefschetz thimble is determined up to homotopy and orientation by the critical point $a$ and the direction $\theta$. When $N = 1$, the homotopy freedom disappears, because $O_1(\C)$ is the discrete group $\{\pm 1\}$.

Lefschetz thimbles for $f$ with direction $\theta$ represent classes in the ``rapid decay homology'' group $H^\theta_N(X,f)$. Roughly speaking, this group describes homology relative to the region where $\Re(e^{-i\theta} f)$ is large and positive. In this context, each thimble integral
\[ \int_{\mathcal{C}}e^{-zf}\,\nu \]
computes the pairing between a rapid decay homology class $\mathcal{C}$ and a ``twisted $1$-form'' $e^{-zf}\,\nu$. When all the critical points of $f$ are non-degenerate, Lefschetz thimbles actually form a basis for $H^\theta_N(X,f)$. As $\theta$ varies, the groups $H^\theta_N(X,f)$ fit together into a local system over the circle of directions, which is singular at the direction of each segment connecting a pair of critical values. The monodromy of this local system can be found using the Picard--Lefschetz formula~\cite[Section~1]{Arnold}\cite[Section~3.3, Part II]{pham}.

Like solutions of level~$1$ ODEs, thimble integrals often exhibit the Stokes phenomenon. The Stokes constants can be interpreted geometrically as intersection numbers for pairs of thimbles. Finding the Stokes constants is equivalent to finding the monodromy of the local system $H^\theta_N(X,f)$.

%%Equivalently, using the Borel regularity result \textcolor{magenta}{[do we really want this theorem, rather than the thimble projection formula?]} Theorem~\ref{thm:maxim}, we can express thimble integrals as Laplace transforms and reconstruct the monodromy of $H^\theta_N(X,f)$ from the associated Stokes constants. The Stokes
%%\color{BlueViolet}
%%\begin{itemize}
%%\item Explain how can be seen in terms of homology (cite Pham).
%%\item the Stokes constants are intersection number of thimbles, computed with Picard Lefschetz formula.
%%\end{itemize}
\color{black}
%
\subsubsection{Asymptotics of thimble integrals}
%
Thimble integrals are traditionally understood through their asymptotics, which can be found with the saddle point approximation. A thimble integral's asymptotic expansion is typically divergent, but the integral contains a hint about where to find the corresponding analytic object: the thimble itself, which is a real-analytic submanifold.

\textcolor{orange}{[Keep revising\ldots]}
\color{BlueViolet}
\begin{itemize}
\item Traditionally, people study the asymptotic expansions of thimble integrals. This is the saddle point approximation.
\item Problem: the resulting series is usually divergent. This is another source of divergent power series.
\item In this case, we have a clue about where to find the corresponding analytic object, because the thimble itself is analytic.
\item In fact, the thimble integral is almost a Laplace transform (cite Pham).
%%\begin{itemize}
%%\item ODE: get a formal series, resum it, check whether the result is an actual series.
%%\item Thimble integral: get a formal series, resum it, check whether the result matches the original analytic thimble integral.
%%\end{itemize}
\end{itemize}
\color{DarkTurquoise}\par
Classical examples of $1$-dimensional thimble integrals (with polynomial $f$) are special functions, thus the Borel summability properties of their asymptotics can be studied either analytically (through the \textit{thimble projection reasoning} see the discussion in Section~\ref{sec:examples}) or geometrically (in terms of a certain Riemann--Hilbert problem \cite{Maxim_slide_ERC}\cite[Section 6.2]{kontsevich2022analyticity}).

@@

\color{RoyalBlue}
\subsubsection*{Old stuff to distribute among new sections}
Thimble integrals have been studied from different perspectives: in physics, they play an important technical role in quantum mechanics, where infinite-dimensional exponential integrals are supposed to give the expectation values of observable quantities \cite{dunne-unsal2,dunne-unsal,Fauvet_Menous_Queva,Tanizaki:2014tua}. In this context, physicists often use Borel summation, resurgence and related techniques to assign values to these integrals going beyond their pertubative expansion (see also \cite{Berry_Howls,Berry1991,costin_kruskal,Howls97,Howls,pham1988resurgence}). For instance, in complex Chern--Simons theory, one could decompose the path integral in thimble integrals and arguing as in the finite dimesional set-up to study the Witten--Reshetikhin--Turaev invariants of $3$ manifolds \cite{gukov-marino-purtrov-resurgence,Witten}. \textcolor{orange}{Take a look at Witten's paper on knots} More generally, we could think of a problem that is known to admit a thimble integral solution but that's hard to be defined explicitly. However, we know the perturbative expansion of the expected solution; then Borel regularity tells us that the Borel sum of the pertubative series is the solution we are looking for. In fact, the Laplace transform ray (namely the ray along which the Laplace trasnform is defined) is often a ``collapsed'' thimble.\textcolor{Maroon}{This is the bit about turning a perturbative series back into a thimble integral, taking advantage of the fact that the Laplace transform ray is often a ``collapsed'' thimble.}

@@

The Laplace transform $\laplace^\theta_{\zeta,\alpha}$ is a homomorphism from the algebra of locally integrable, exponentially bounded holomorphic functions, equipped with the convolution product, to the algebra of analytic functions on the half-plane $\Re(e^{i\theta} z) > 0$, equipped with the usual product.

@@

\textcolor{orange}{[add proof for $\alpha\neq 0$]}
    \laplace_{\zeta,\alpha}[{\phi}\ast_{\zeta,\alpha}{\psi}](a)&= \int_{\mathcal{J}^\theta_{\zeta, \alpha}} e^{-z\zeta(a)} \left(\int_{\zeta=\alpha}^a \psi \mathsf{R}^*\phi\;d\zeta\right)\;d\zeta

    \begin{align*}
         \laplace_{\zeta,\alpha}[{\phi}]\,\laplace_{\zeta,\alpha}[{\psi}]&=\int_\alpha^\infty e^{-z t}\phi(t)dt \int_\alpha^\infty e^{-z u} \psi(u) du \\
         &=\int_\alpha^\infty \left(\int_\alpha^\infty  e^{-z (t+u)}\phi(t) \psi(u) du \right)dt \\
         &=\int_\alpha^\infty \left(\int_{t+\alpha}^\infty   e^{-z s} \psi(s-t) \phi(t) ds \right)dt 
    \end{align*}
    Define $\psi(s)=0$ if $s<\alpha$, thus $\psi(s-t)=0$ if $s<t+\alpha$, 
    \begin{align*}
        \int_\alpha^\infty \left(\int_{t+\alpha}^\infty   e^{-z s} \psi(s-t) \phi(t) ds \right)dt &=\int_\alpha^\infty \left(\int_{\alpha}^\infty   e^{-z s} \psi(s-t) \phi(t) ds \right)dt 
    \end{align*}
    Under the assumption that the integral is absolutely convergent, we can exchange the order of integration
    \begin{align*}
        \int_\alpha^\infty \left(\int_{\alpha}^\infty   e^{-z s} \psi(s-t) \phi(t) ds \right)dt &=\int_\alpha^\infty e^{-z s} \left(\int_{\alpha}^\infty    \psi(s-t) \phi(t) dt \right)ds\\
        &=\int_\alpha^\infty e^{-z s} \left(\int_{\alpha}^s    \psi(s-t) \phi(t) dt \right)ds \\
        &=\int_\alpha^\infty e^{-z s} \phi\ast_{t,\alpha}\psi ds 
    \end{align*}
    \textcolor{orange}{[see Thm 5.25 \cite{diverg-resurg-i}]}
\end{verify}
\end{proof}
%
\begin{remark}
For $\alpha=0$, the Definition~\label{def:convolution} agrees with the standard deifinition of convolution \cite[Definition~5.12]{diverg-resurg-i}.
In addition, we will denote $\ast_{\zeta,0}$ simply by \textcolor{magenta}{$\ast_\zeta$ [coordinate added]}, following the standard convention.   
\end{remark}
Notice that, assuming the Taylor expansion of $\phi$ and $\psi$ at $\zeta=\alpha$ are convergent in a disk of radius $R$, then the convolution $\phi\ast_{\zeta,\alpha}\psi$ has a convergent Taylor expansion at $\zeta=\alpha$ in the disk of radius $R$ (when $\alpha=0$, see \cite[Lemma 5.14]{diverg-resurg-i} for a proof).
